---
title: "Final Project: Data Analysis"
author: "Experiments and Causality"
output: 
    github_document: default
    pdf_document: default
knit: (function(inputFile, encoding) {
  rmarkdown::render(
    inputFile, encoding = encoding,
    output_format = c('github_document', 'pdf_document')) 
    })
---

# Import Libraries

```{r, message=FALSE}
library(data.table)
library(stargazer)
library(dplyr)
library(foreign)
library(knitr)
library(lmtest)
library(sandwich)
```

# Load Data

First, we need to convert some string fields explicitly into factor fields
```{r}
d_raw <- fread('./data_v2_processed.csv')
d_raw[,gender:=as.factor(gender)]
d_raw[,gender_shown:=as.factor(gender_shown)]
d_raw[,age:=as.factor(age)]
d_raw[,years_programming:=as.factor(years_programming)]
d_raw[,years_javascript:=as.factor(years_javascript)]
d_raw[,num_crs_per_week:=as.factor(num_crs_per_week)]
d_raw[,education:=as.factor(education)]
d_raw[,employment:=as.factor(employment)]
```

# EDA
First, we get some columns of interest.
```{r}
numeric_covariates = c('pct_men') 
numeric_responses = c('code_quality', 'num_bugs', 'num_quality', 'num_texts')
numeric_variables = c(numeric_covariates, numeric_responses)
covariates_of_interest = c('gender', 'age', 'years_programming', 'years_javascript', 
                           'num_crs_per_week', 'education', 'employment', numeric_covariates)
variables_of_interest = c(covariates_of_interest, 'gender_shown', numeric_responses, 'duration')
```

## Check for Missing Values
We have some missing values in our data. Notably two rows that we don't have any covariate information for. This was likely a fluke in the collection system.

```{r}
d_raw_covariates_missing = d_raw[,..covariates_of_interest] == ''
d_raw_covariates_missing[is.na(d_raw_covariates_missing)] = TRUE

d = d_raw[!(rowSums(d_raw_covariates_missing) == 8)]
d[,is_male_treatment:=as.integer(d$gender_shown=='Male')]
```

## Randomization Check
Next, we check that our randomization worked. To do this, we do a summary of our covariates split by the treatment (TODO: we need to do something more systematic here - perhaps a regression)
```{r}
# summary of each by treatment - should have a more systematic way of checking covariates
summary(d[gender_shown == 'Male', ..covariates_of_interest])
summary(d[gender_shown == 'Female', ..covariates_of_interest])
```

Doing somethign slightly more systematic, we use the covariates to predict gender to see if there is any covariate imbalance.
```{r}
lm_covariates = d[,lm(gender_shown == "Male" ~ gender + age + years_programming + years_javascript + num_crs_per_week + education + employment + pct_men)]
summary(lm_covariates)
```

We have a high p-value, indicating that we have confidence that the covariates are balanced.

## Histogram of numeric fields
```{r}
par(mfrow=c(2,2))
for (cov in numeric_covariates) {
  d_raw[,hist(get(cov), main=paste('Histogram of ', cov), xlab=cov)]  
}
```

# Regression
```{r}
lm1 = d[,lm(num_lines ~ gender_shown)]
summary(lm1)

lm2 = d[,lm(code_quality ~ gender_shown)]
summary(lm2)

lm3 = d[,lm(num_lines ~ gender_equal)]
summary(lm3)

lm4 = d[,lm(code_quality ~ gender_equal)]
summary(lm4)
```
```{r}
lm1 = d[,lm(`Duration (in seconds)` ~ gender_shown + years_programming)]
summary(lm1)

lm2 = d[,lm(num_quality ~ gender_shown + years_programming)]
summary(lm2)

lm3 = d[,lm(num_bugs ~ gender_shown + years_programming)]
summary(lm3)

lm4 = d[,lm(num_quality/num_lines ~ gender_shown + years_programming)]
summary(lm4)

lm5 = d[,lm(num_bugs/num_lines ~ gender_shown + years_programming)]
summary(lm5)

```
```{r}
hist(d$is_male_treatment)
```

