---
title: "Final Project: Data Analysis"
author: "Experiments and Causality"
output: 
    github_document: default
    pdf_document: default
knit: (function(inputFile, encoding) {
  rmarkdown::render(
    inputFile, encoding = encoding,
    output_format = c('github_document', 'pdf_document')) 
    })
---

# Import Libraries

```{r, message=FALSE}
library(data.table)
library(stargazer)
library(dplyr)
library(foreign)
library(knitr)
library(lmtest)
library(sandwich)
library(ggplot2)
library(pwr)
```

```{r}
# Power Analysis
u=8
v=100-u-1
f2=.3/(1-.3)
sig = .01

pwr.f2.test(u = u, v = v, f2 = f2, sig.level = 0.01)
```


# Load Data

First, we need to convert some string fields explicitly into factor fields
```{r}
years_programming_levels = c("0 years", "<1 year", "1-2 years", "3-5 years", "5-10 years", "10-15 years", "15-20 years", "NA")
years_javascript_levels = c("0 years", "<1 year", "1-2 years", "3-5 years", "5-10 years", "10-15 years", "15-20 years", "NA")
education_levels = c("Less than high school", "High school graduate", "Some college", "4 year degree", "Professional degree")
d_raw <- fread('./data_v3_processed.csv')
d_raw[,gender:=relevel(as.factor(gender),"Male")]
d_raw[,gender_shown:=relevel(as.factor(gender_shown),"Male")]
d_raw[,age:=relevel(as.factor(age),"18 - 24")]
d_raw[,years_programming:=relevel(factor(years_programming, levels=years_programming_levels), "0 years")]
d_raw[,years_javascript:=relevel(factor(years_javascript, levels=years_javascript_levels), "0 years")]
d_raw[,num_crs_per_week:=relevel(as.factor(num_crs_per_week), "Never")]
d_raw[,education:=relevel(factor(education, levels=education_levels), "Less than high school")]
d_raw[,employment:=relevel(as.factor(employment), "Unemployed / Student")]
d_raw[,time_taken:=`Duration (in seconds)`]
```

For ease of evaluation, let's also add a variable: ratio of men to women in the workplace.
```{r}
d_raw[,ratio_men_to_women:=pct_men/(100-pct_men)]
d_raw[ratio_men_to_women == Inf,ratio_men_to_women := 100]
```

# EDA
First, we get some columns of interest.
```{r}
numeric_covariates = c('pct_men', 'ratio_men_to_women') 
numeric_responses = c('code_quality', 'num_bugs', 'num_quality', 'num_texts', 
                      'percent_bugs', 'percent_quality', 'time_taken', 
                      'num_positive_comments', 'num_negative_comments', 'percent_positive_comments',
                      'percent_negative_comments', 'num_subjective_comments', 'percent_subjective_comments')
numeric_variables = c(numeric_covariates, numeric_responses)
attn_variables = c('correct_app', 'correct_company', 'correct_gender', 'correct_name')
covariates_of_interest = c('gender', 'age', 'years_programming', 'years_javascript', 
                           'num_crs_per_week', 'education', 'employment', numeric_covariates)
variables_of_interest = c(covariates_of_interest, 'gender_shown', numeric_responses)
```

## Check for Missing Values
We have some missing values in our data. Notably years programming and years javascript, where we forgot to make the questions required. Given this, we will put them into their own "NA" category.

```{r}
summary(d_raw)
d_raw[is.na(years_programming), years_programming := "NA"]
d_raw[is.na(years_javascript),  years_javascript:= "NA"]
d_raw[,years_programming:=relevel(factor(years_programming, levels=years_programming_levels), "0 years")]
d_raw[,years_javascript:=relevel(factor(years_javascript, levels=years_javascript_levels), "0 years")]
d = d_raw
```

## Covariate Analysis
```{r}
for (covariate in covariates_of_interest) {
  print(ggplot(d, aes_string(x = covariate)) + 
    geom_bar() + ggtitle(paste("Distribution of", covariate)) + xlab(covariate))
}
summary(d[,..covariates_of_interest])
```

Things that were not good: years_programming and years_javascript had some NAs because we did not make them required.

## Check Attention Checks
```{r}
summary(d[,..attn_variables])
summary(d[gender_shown=='Female',..attn_variables])
summary(d[gender_shown=='Male',..attn_variables])
ggplot(d, aes(x = factor(correct_gender), fill=gender_shown)) + 
  geom_bar(position = position_dodge()) + ggtitle("Gender Attention Check") + xlab("Remembered Gender?")
ggplot(d, aes(x = factor(correct_company), fill=gender_shown)) + 
  geom_bar(position = position_dodge()) + ggtitle("Company Attention Check") + xlab("Remembered Company?")
ggplot(d, aes(x = factor(correct_app), fill=gender_shown)) + 
  geom_bar(position = position_dodge()) + ggtitle("App Attention Check") + xlab("Remembered App?")
ggplot(d, aes(x = factor(correct_name), fill=gender_shown)) + 
  geom_bar(position = position_dodge()) + ggtitle("Name Attention Check") + xlab("Remembered Name?")
```

## Randomization Check
Next, we check that our randomization worked. To do this, we do a summary of our covariates split by the treatment
```{r}
# summary of each by treatment - should have a more systematic way of checking covariates
for (covariate in covariates_of_interest) {
  print(ggplot(d, aes_string(x = covariate, fill="gender_shown")) + 
    geom_bar(position='dodge') + ggtitle(paste("Distribution of", covariate)) + xlab(covariate))
}
```

Doing something slightly more systematic, we use the covariates to predict gender to see if there is any covariate imbalance.

```{r}
lm_covariates = d[,lm(gender_shown == "Male" ~ gender + age + years_programming + years_javascript + num_crs_per_week + education + employment + pct_men)]
summary(lm_covariates)
```

We have a decently high p-value, indicating that we have confidence that the covariates are balanced.

## Histogram of numeric fields
```{r}
par(mfrow=c(2,2))
for (cov in numeric_variables) {
  d_raw[,hist(get(cov), main=paste('Histogram of ', cov), xlab=cov)]  
}
```

## Negative v. Positive Comments
```{r}
hist(d[, num_negative_comments], col=rgb(0,0,1,0.10), xlim=c(0,10), ylim=c(0,30), breaks=c(-0.5,0.5,1.5,2.5,3.5,4.5,5.5,6.5,7.5,8.5,9.5,10.5), main="Histogram of Number of Comments by Sentiment", xlab="Number of Comments")
hist(d[, num_positive_comments], col=rgb(1,0,0,0.10), xlim=c(0,10), ylim=c(0,30), breaks=c(-0.5,0.5,1.5,2.5,3.5,4.5,5.5,6.5,7.5,8.5,9.5,10.5), add=T)
legend(x=7, y=20, legend=c("Negative Comments", "Positive Comments"),
       col=c("blue", "red"), lty=1, cex=0.8)
```

# Results by Gender
```{r}
hist(d[gender_shown=="Female", num_lines], col=rgb(0,0,1,.25), xlim=c(0,20), ylim=c(0,10), breaks=20, main="Histogram of Number of Comments by Gender Shown", xlab="Number of Comments")
hist(d[gender_shown=="Male", num_lines], col=rgb(1,0,0,.25), xlim=c(0,20), ylim=c(0,10), breaks=20, add=T)
legend(x=14, y=8, legend=c("Female Treatment", "Male Treatment", "Overlap"),
       col=c(rgb(0,0,1,0.5), rgb(1,0,0,0.5), col=rgb(1,0,1,.5)), lty=1, cex=0.8)


print(ggplot(d, aes_string(x = "num_lines", fill="gender_shown")) + 
  geom_bar(position='dodge') + ggtitle(paste("Distribution of Code Comments")) + xlab("Number of Comments"))
```

```{r}
hist(d[gender_shown=="Female", num_quality], col=rgb(0,0,1,.25), xlim=c(0,20), ylim=c(0,10), breaks=15, main="Histogram of Number of Quality/Opinion Comments by Gender Shown", xlab="Number of Comments")
hist(d[gender_shown=="Male", num_quality], col=rgb(1,0,0,.25), xlim=c(0,20), ylim=c(0,10), breaks=15, add=T)
legend(x=14, y=8, legend=c("Female Treatment", "Male Treatment", "Overlap"),
       col=c(rgb(0,0,1,0.5), rgb(1,0,0,0.5), col=rgb(1,0,1,.5)), lty=1, cex=0.8)
```


```{r}
hist(d[gender_shown=="Female", code_quality], col=rgb(0,0,1,1/4), xlim=c(1,10), ylim=c(0,10), breaks=10, main="Histogram of Code Quality by Gender Shown", xlab="Code Quality (1-10)")
hist(d[gender_shown=="Male", code_quality], col=rgb(1,0,0,1/4), xlim=c(1,10), ylim=c(0,10), breaks=10, add=T)
legend(x=7, y=8, legend=c("Female Treatment", "Male Treatment"),
       col=c("blue", "red"), lty=1, cex=0.8)
```

```{r}
for (covariate in numeric_variables) {
  if (covariate == "Duration (in seconds)") {
    next
  }
  print(ggplot(d, aes_string(x = covariate, fill="gender_shown")) + 
    geom_bar(position='dodge') + ggtitle(paste("Distribution of", covariate)) + xlab(covariate))
}

```


# Regression
```{r}
get_se_robust <- function(model) { 
  ses <- sqrt(diag(vcovHC(model, type="HC")))
  return(ses)
}
```

```{r}
# Simplest Regressions for Primary Outcome Measures
lm_lines = d[,lm(num_lines ~ gender_shown)]
lm_q_lines = d[,lm(num_quality ~ gender_shown)]
lm_code_quality = d[,lm(code_quality ~ gender_shown)]

se_basic = list(get_se_robust(lm_lines), get_se_robust(lm_q_lines), get_se_robust(lm_code_quality))
stargazer(lm_lines, lm_q_lines, lm_code_quality, se=se_basic, type="text")
```

```{r}
# Regressions for Primary Outcome Measures with Reviewer Gender
d[,is_reviewer_female := gender == 'Female']

lm_lines = d[,lm(num_lines ~ gender_shown + is_reviewer_female)]
lm_q_lines = d[,lm(num_quality ~ gender_shown + is_reviewer_female)]
lm_code_quality = d[,lm(code_quality ~ gender_shown + is_reviewer_female)]

se_basic_w_gender = list(get_se_robust(lm_lines), get_se_robust(lm_q_lines), get_se_robust(lm_code_quality))
stargazer(lm_lines, lm_q_lines, lm_code_quality, se=se_basic_w_gender, type="text")
```


```{r}
getRobustCoefTest <- function(r) {
  coeftest(r, vcov = vcovHC(lm, type="HC"))
}
```

## Number of Comments
```{r}
lm = d[,lm(num_lines ~ gender_shown)]
getRobustCoefTest(lm)
```

```{r}
lm = d[,lm(num_lines ~ gender_shown + is_reviewer_female + age + years_programming + years_javascript + num_crs_per_week + education + employment + pct_men)]
getRobustCoefTest(lm)['gender_shownFemale',]
```

### Interaction Effects
```{r}
lm = d[,lm(num_lines ~ gender_shown + gender_shown*is_reviewer_female + age + years_programming + years_javascript + num_crs_per_week + education + employment + pct_men)]
getRobustCoefTest(lm)[c('gender_shownFemale', 'is_reviewer_femaleTRUE'),]
```

```{r}
lm = d[,lm(num_lines ~ gender_shown + is_reviewer_female + age + gender_shown*years_programming + years_programming + years_javascript + num_crs_per_week + education + employment + pct_men)]
getRobustCoefTest(lm)[c('gender_shownFemale', 'gender_shownFemale:years_programming3-5 years',
                        'gender_shownFemale:years_programming5-10 years', 'gender_shownFemale:years_programming10-15 years'),]
summary(lm)

```

```{r}

d[, years_programming_1_2_years:=as.integer(years_programming == '1-2 years')]
d[, years_programming_3_5_years:=as.integer(years_programming == '3-5 years')]
d[, years_programming_5_10_years:=as.integer(years_programming == '5-10 years')]

d[, num_crs_per_week_0_1:=as.integer(num_crs_per_week == '0-1 times per week')]
d[, num_crs_per_week_1_3:=as.integer(num_crs_per_week == '1-3 times per week')]
d[, num_crs_per_week_4_7:=as.integer(num_crs_per_week == '4-7 times per week')]
d[, num_crs_per_week_7_plus:=as.integer(num_crs_per_week == 'More than 7 times per week')]

d[, years_javascript_1_3:=as.integer(years_javascript == '1-2 years')]
d[, years_javascript_3_5:=as.integer(years_javascript == '3-5 years')]
d[, years_javascript_5_10:=as.integer(years_javascript == '5-10 years')]
d[, years_javascript_10_15:=as.integer(years_javascript == '10-15 years')]

d[, has_javascript_exp:=as.integer(grepl('-', years_javascript) )]
d[, is_female_treatment:=as.integer(gender_shown == 'Female')]


lm_lines = d[,lm(num_lines ~ gender_shown + is_reviewer_female 
          + years_programming_1_2_years 
          + years_programming_3_5_years 
          + years_programming_5_10_years 
           + pct_men
           + num_crs_per_week_1_3
           + num_crs_per_week_4_7
           + num_crs_per_week_7_plus
           + years_javascript_1_3
           + years_javascript_3_5
           + years_javascript_5_10
           + years_javascript_10_15
           )]
#getRobustCoefTest(lm)[c('gender_shownFemale', 'gender_shownFemale:years_programming3-5 years',
#                        'gender_shownFemale:years_programming5-10 years', 'gender_shownFemale:years_programming10-15 years'),]


se_num_lines_w_cov = list(get_se_robust(lm_s))
stargazer(lm_s, se=se_num_lines_w_cov, type="text")

anova(lm, lm_s)
table(d$treat)
```

```{r}
# Pruned bins
lm_lines = d[,lm(num_lines ~ gender_shown + is_reviewer_female 
          + gender_equal
          + years_programming_1_2_years 
          + years_programming_3_5_years 
          + years_programming_5_10_years 
           + pct_men
           + num_crs_per_week_1_3
           + num_crs_per_week_4_7
           + num_crs_per_week_7_plus
           + years_javascript_1_3
           + years_javascript_3_5
           + years_javascript_5_10
           + years_javascript_10_15
          
           )]

lm_quality_lines = d[,lm(num_quality ~ gender_shown + is_reviewer_female 
          + gender_equal
          + years_programming_1_2_years 
          + years_programming_3_5_years 
          + years_programming_5_10_years 
           + pct_men
           + num_crs_per_week_1_3
           + num_crs_per_week_4_7
           + num_crs_per_week_7_plus
           + years_javascript_1_3
           + years_javascript_3_5
           + years_javascript_5_10
           + years_javascript_10_15
           )]

lm_code_quality = d[,lm(code_quality ~ gender_shown + is_reviewer_female 
          + gender_equal
          + years_programming_1_2_years 
          + years_programming_3_5_years 
          + years_programming_5_10_years 
           + pct_men
           + num_crs_per_week_1_3
           + num_crs_per_week_4_7
           + num_crs_per_week_7_plus
           + years_javascript_1_3
           + years_javascript_3_5
           + years_javascript_5_10
           + years_javascript_10_15
           )]


se_w_cov = list(get_se_robust(lm_lines), get_se_robust(lm_quality_lines), get_se_robust(lm_code_quality))
stargazer(lm_lines, lm_quality_lines, lm_code_quality, se=se_w_cov, type="text")
```

```{r}
# Including all NA responses
lm_lines = d[,lm(num_lines ~ gender_shown + is_reviewer_female 
          + gender_equal
          + years_programming
          + pct_men
          + num_crs_per_week
          + years_javascript
           )]

lm_quality_lines = d[,lm(num_quality ~ gender_shown + is_reviewer_female 
          + gender_equal
          + years_programming
          + pct_men
          + num_crs_per_week
          + years_javascript
           )]

lm_code_quality = d[,lm(code_quality ~ gender_shown + is_reviewer_female 
          + gender_equal
          + years_programming
          + pct_men
          + num_crs_per_week
          + years_javascript
           )]


se_w_cov = list(get_se_robust(lm_lines), get_se_robust(lm_quality_lines), get_se_robust(lm_code_quality))
stargazer(lm_lines, lm_quality_lines, lm_code_quality, se=se_w_cov, type="text")
```

```{r}
lm = d[,lm(num_lines ~ gender_shown + is_reviewer_female + age + gender_shown*years_javascript + years_programming + years_javascript + num_crs_per_week + education + employment + pct_men)]
getRobustCoefTest(lm)[c('gender_shownFemale', 'gender_shownFemale:years_javascript1-2 years',
                        'gender_shownFemale:years_javascript3-5 years',
                        'gender_shownFemale:years_javascript5-10 years', 
                        'gender_shownFemale:years_javascript10-15 years'),]
```

```{r}
lm = d[,lm(num_lines ~ gender_shown + is_reviewer_female + age + years_programming + years_javascript + num_crs_per_week + education + gender_shown*employment + pct_men)]
getRobustCoefTest(lm)[c('gender_shownFemale', 'gender_shownFemale:employmentEmployed by:'),]
```

```{r}
lm = d[,lm(num_lines ~ gender_shown + is_reviewer_female + age + years_programming + years_javascript + num_crs_per_week + education + employment + gender_shown*pct_men)]
getRobustCoefTest(lm)[c('gender_shownFemale', 'gender_shownFemale:pct_men'),]
```

## Code Quality
```{r}
lm = d[,lm(code_quality ~ gender_shown)]
getRobustCoefTest(lm)
```

```{r}
lm = d[,lm(code_quality ~ gender_shown + is_reviewer_female + age + years_programming + years_javascript + num_crs_per_week + education + employment + pct_men)]
getRobustCoefTest(lm)['gender_shownFemale',]
```

### Interaction Effects
```{r}
lm = d[,lm(code_quality ~ gender_shown + gender_shown*is_reviewer_female + age + years_programming + years_javascript + num_crs_per_week + education + employment + pct_men)]
getRobustCoefTest(lm)[c('gender_shownFemale', 'gender_shownFemale:genderFemale'),]
```

```{r}
lm = d[,lm(code_quality ~ gender_shown + is_reviewer_female + age + gender_shown*years_programming + years_javascript + num_crs_per_week + education + employment + pct_men)]
getRobustCoefTest(lm)[c('gender_shownFemale', 'gender_shownFemale:years_programming3-5 years',
                        'gender_shownFemale:years_programming5-10 years', 'gender_shownFemale:years_programming10-15 years'),]
```

```{r}
lm = d[,lm(code_quality ~ gender_shown + is_reviewer_female + age + gender_shown*years_javascript + years_programming + years_javascript + num_crs_per_week + education + employment + pct_men)]
getRobustCoefTest(lm)[c('gender_shownFemale', 'gender_shownFemale:years_javascript1-2 years',
                        'gender_shownFemale:years_javascript3-5 years',
                        'gender_shownFemale:years_javascript5-10 years', 
                        'gender_shownFemale:years_javascript10-15 years'),]
```

```{r}
#lm = d[,lm(code_quality ~ gender_shown + gender + age + years_programming + years_javascript + num_crs_per_week + education + gender_shown*employment + pct_men)]
#getRobustCoefTest(lm)[c('gender_shownFemale', 'gender_shownFemale:employmentEmployed by:'),]
```

```{r}
lm = d[,lm(code_quality ~ gender_shown + is_reviewer_female + age + years_programming + years_javascript + num_crs_per_week + education + employment + gender_shown*pct_men)]
getRobustCoefTest(lm)[c('gender_shownFemale', 'gender_shownFemale:pct_men'),]
```


```{r}
#lm$vcovHC_ <- vcovHC(lm)
#stargazer(lm, se=list(sqrt(diag(lm$vcovHC_))), type="text")
stargazer(lm, type="text")
```


```{r}
lm = d[,lm(code_quality ~ gender_shown + is_reviewer_female + age + years_programming + years_javascript + num_crs_per_week + education + employment + gender_shown*ratio_men_to_women)]
getRobustCoefTest(lm)[c('gender_shownFemale', 'gender_shownFemale:ratio_men_to_women'),]
```

```{r}
lm = d[,lm(code_quality ~ gender_shown + is_reviewer_female + age + years_programming + years_javascript + num_crs_per_week + education + employment + gender_shown*log(ratio_men_to_women))]
getRobustCoefTest(lm)[c('gender_shownFemale', 'gender_shownFemale:log(ratio_men_to_women)'),]
```

## Percent Bugs
```{r}
lm = d[,lm(percent_bugs ~ gender_shown)]
getRobustCoefTest(lm)
```

```{r}
lm = d[,lm(percent_bugs ~ gender_shown + is_reviewer_female + age + years_programming + years_javascript + num_crs_per_week + education + employment + pct_men)]
getRobustCoefTest(lm)['gender_shownFemale',]
```

### Interaction Effects
```{r}
lm = d[,lm(percent_bugs ~ gender_shown + gender_shown*is_reviewer_female + age + years_programming + years_javascript + num_crs_per_week + education + employment + pct_men)]
getRobustCoefTest(lm)[c('gender_shownFemale', 'gender_shownFemale:genderFemale'),]
```

```{r}
lm = d[,lm(percent_bugs ~ gender_shown + is_reviewer_female + age + gender_shown*years_programming + years_javascript + num_crs_per_week + education + employment + pct_men)]
getRobustCoefTest(lm)[c('gender_shownFemale', 'gender_shownFemale:years_programming3-5 years',
                        'gender_shownFemale:years_programming5-10 years', 'gender_shownFemale:years_programming10-15 years'),]
```

```{r}
lm = d[,lm(percent_bugs ~ gender_shown + is_reviewer_female + age + gender_shown*years_javascript + years_programming + years_javascript + num_crs_per_week + education + employment + pct_men)]
getRobustCoefTest(lm)[c('gender_shownFemale', 'gender_shownFemale:years_javascript1-2 years',
                        'gender_shownFemale:years_javascript3-5 years',
                        'gender_shownFemale:years_javascript5-10 years', 
                        'gender_shownFemale:years_javascript10-15 years'),]
```

```{r}
lm = d[,lm(percent_bugs ~ gender_shown + is_reviewer_female + age + years_programming + years_javascript + num_crs_per_week + education + gender_shown*employment + pct_men)]
getRobustCoefTest(lm)[c('gender_shownFemale', 'gender_shownFemale:employmentEmployed by:'),]
```

```{r}
lm = d[,lm(percent_bugs ~ gender_shown + is_reviewer_female + age + years_programming + years_javascript + num_crs_per_week + education + employment + gender_shown*pct_men)]
getRobustCoefTest(lm)[c('gender_shownFemale', 'gender_shownFemale:pct_men'),]
```

## Time Taken
```{r}
lm = d[,lm(`Duration (in seconds)` ~ gender_shown)]
getRobustCoefTest(lm)
```

```{r}
lm = d[,lm(`Duration (in seconds)` ~ gender_shown + is_reviewer_female + age + years_programming + years_javascript + num_crs_per_week + education + employment + pct_men)]
getRobustCoefTest(lm)['gender_shownFemale',]
```

### Interaction Effects
```{r}
lm = d[,lm(`Duration (in seconds)` ~ gender_shown + gender_shown*is_reviewer_female + age + years_programming + years_javascript + num_crs_per_week + education + employment + pct_men)]
getRobustCoefTest(lm)[c('gender_shownFemale', 'gender_shownFemale:genderFemale'),]
```

```{r}
lm = d[,lm(`Duration (in seconds)` ~ gender_shown + is_reviewer_female + age + gender_shown*years_programming + years_javascript + num_crs_per_week + education + employment + pct_men)]
getRobustCoefTest(lm)[c('gender_shownFemale', 'gender_shownFemale:years_programming3-5 years',
                        'gender_shownFemale:years_programming5-10 years', 'gender_shownFemale:years_programming10-15 years'),]
```

```{r}
lm = d[,lm(`Duration (in seconds)` ~ gender_shown + is_reviewer_female + age + gender_shown*years_javascript + years_programming + years_javascript + num_crs_per_week + education + employment + pct_men)]
getRobustCoefTest(lm)[c('gender_shownFemale', 'gender_shownFemale:years_javascript1-2 years',
                        'gender_shownFemale:years_javascript3-5 years',
                        'gender_shownFemale:years_javascript5-10 years', 
                        'gender_shownFemale:years_javascript10-15 years'),]
```

```{r}
lm = d[,lm(`Duration (in seconds)` ~ gender_shown + is_reviewer_female + age + years_programming + years_javascript + num_crs_per_week + education + gender_shown*employment + pct_men)]
getRobustCoefTest(lm)[c('gender_shownFemale', 'gender_shownFemale:employmentEmployed by:'),]
```

```{r}
lm = d[,lm(`Duration (in seconds)` ~ gender_shown + is_reviewer_female + age + years_programming + years_javascript + num_crs_per_week + education + employment + gender_shown*pct_men)]
getRobustCoefTest(lm)[c('gender_shownFemale', 'gender_shownFemale:pct_men'),]
```

## Number of Positive Comments
```{r}
lm = d[,lm(num_positive_comments ~ gender_shown)]
getRobustCoefTest(lm)
```

```{r}
lm = d[,lm(num_positive_comments ~ gender_shown + gender + age + years_programming + years_javascript + num_crs_per_week + education + employment + pct_men)]
getRobustCoefTest(lm)['gender_shownFemale',]
```

### Interaction Effects
```{r}
lm = d[,lm(num_positive_comments ~ gender_shown + gender_shown*gender + age + years_programming + years_javascript + num_crs_per_week + education + employment + pct_men)]
getRobustCoefTest(lm)[c('gender_shownFemale', 'gender_shownFemale:genderFemale'),]
```

```{r}
lm = d[,lm(num_positive_comments ~ gender_shown + gender + age + gender_shown*years_programming + years_javascript + num_crs_per_week + education + employment + pct_men)]
getRobustCoefTest(lm)[c('gender_shownFemale', 'gender_shownFemale:years_programming3-5 years',
                        'gender_shownFemale:years_programming5-10 years', 'gender_shownFemale:years_programming10-15 years'),]
```

```{r}
lm = d[,lm(num_positive_comments ~ gender_shown + gender + age + gender_shown*years_javascript + years_programming + years_javascript + num_crs_per_week + education + employment + pct_men)]
getRobustCoefTest(lm)[c('gender_shownFemale', 'gender_shownFemale:years_javascript1-2 years',
                        'gender_shownFemale:years_javascript3-5 years',
                        'gender_shownFemale:years_javascript5-10 years', 
                        'gender_shownFemale:years_javascript10-15 years'),]
```

```{r}
lm = d[,lm(num_positive_comments ~ gender_shown + gender + age + years_programming + years_javascript + num_crs_per_week + education + gender_shown*employment + pct_men)]
getRobustCoefTest(lm)[c('gender_shownFemale', 'gender_shownFemale:employmentEmployed by:'),]
```

```{r}
lm = d[,lm(num_positive_comments ~ gender_shown + gender + age + years_programming + years_javascript + num_crs_per_week + education + employment + gender_shown*pct_men)]
getRobustCoefTest(lm)[c('gender_shownFemale', 'gender_shownFemale:pct_men'),]
```

```{r}
lm = d[,lm(num_positive_comments ~ gender_shown + gender + age + years_programming + years_javascript + num_crs_per_week + education + employment + gender_shown*ratio_men_to_women)]
getRobustCoefTest(lm)[c('gender_shownFemale', 'gender_shownFemale:ratio_men_to_women'),]
```

## Number of Negative Comments
```{r}
lm = d[,lm(num_negative_comments ~ gender_shown)]
getRobustCoefTest(lm)
```

```{r}
lm = d[,lm(num_negative_comments ~ gender_shown + gender + age + years_programming + years_javascript + num_crs_per_week + education + employment + pct_men)]
getRobustCoefTest(lm)['gender_shownFemale',]
```

### Interaction Effects
```{r}
lm = d[,lm(num_negative_comments ~ gender_shown + gender_shown*gender + age + years_programming + years_javascript + num_crs_per_week + education + employment + pct_men)]
getRobustCoefTest(lm)[c('gender_shownFemale', 'gender_shownFemale:genderFemale'),]
```

```{r}
lm = d[,lm(num_negative_comments ~ gender_shown + gender + age + gender_shown*years_programming + years_javascript + num_crs_per_week + education + employment + pct_men)]
getRobustCoefTest(lm)[c('gender_shownFemale', 'gender_shownFemale:years_programming3-5 years',
                        'gender_shownFemale:years_programming5-10 years', 'gender_shownFemale:years_programming10-15 years'),]
```

```{r}
lm = d[,lm(num_negative_comments ~ gender_shown + gender + age + gender_shown*years_javascript + years_programming + years_javascript + num_crs_per_week + education + employment + pct_men)]
getRobustCoefTest(lm)[c('gender_shownFemale', 'gender_shownFemale:years_javascript1-2 years',
                        'gender_shownFemale:years_javascript3-5 years',
                        'gender_shownFemale:years_javascript5-10 years', 
                        'gender_shownFemale:years_javascript10-15 years'),]
```

```{r}
lm = d[,lm(num_negative_comments ~ gender_shown + gender + age + years_programming + years_javascript + num_crs_per_week + education + gender_shown*employment + pct_men)]
getRobustCoefTest(lm)[c('gender_shownFemale', 'gender_shownFemale:employmentEmployed by:'),]
```

```{r}
lm = d[,lm(num_negative_comments ~ gender_shown + gender + age + years_programming + years_javascript + num_crs_per_week + education + employment + gender_shown*pct_men)]
getRobustCoefTest(lm)[c('gender_shownFemale', 'gender_shownFemale:pct_men'),]
```

```{r}
lm = d[,lm(num_negative_comments ~ gender_shown + gender + age + years_programming + years_javascript + num_crs_per_week + education + employment + gender_shown*ratio_men_to_women)]
getRobustCoefTest(lm)[c('gender_shownFemale', 'gender_shownFemale:ratio_men_to_women'),]
```

## Number of Subjective Comments
```{r}
lm = d[,lm(num_subjective_comments ~ gender_shown)]
getRobustCoefTest(lm)
```

```{r}
lm = d[,lm(num_subjective_comments ~ gender_shown + gender + age + years_programming + years_javascript + num_crs_per_week + education + employment + pct_men)]
getRobustCoefTest(lm)['gender_shownFemale',]
```

### Interaction Effects
```{r}
lm = d[,lm(num_subjective_comments ~ gender_shown + gender_shown*gender + age + years_programming + years_javascript + num_crs_per_week + education + employment + pct_men)]
getRobustCoefTest(lm)[c('gender_shownFemale', 'gender_shownFemale:genderFemale'),]
```

```{r}
lm = d[,lm(num_subjective_comments ~ gender_shown + gender + age + gender_shown*years_programming + years_javascript + num_crs_per_week + education + employment + pct_men)]
getRobustCoefTest(lm)[c('gender_shownFemale', 'gender_shownFemale:years_programming3-5 years',
                        'gender_shownFemale:years_programming5-10 years', 'gender_shownFemale:years_programming10-15 years'),]
```

```{r}
lm = d[,lm(num_subjective_comments ~ gender_shown + gender + age + gender_shown*years_javascript + years_programming + years_javascript + num_crs_per_week + education + employment + pct_men)]
getRobustCoefTest(lm)[c('gender_shownFemale', 'gender_shownFemale:years_javascript1-2 years',
                        'gender_shownFemale:years_javascript3-5 years',
                        'gender_shownFemale:years_javascript5-10 years', 
                        'gender_shownFemale:years_javascript10-15 years'),]
```

```{r}
lm = d[,lm(num_subjective_comments ~ gender_shown + gender + age + years_programming + years_javascript + num_crs_per_week + education + gender_shown*employment + pct_men)]
getRobustCoefTest(lm)[c('gender_shownFemale', 'gender_shownFemale:employmentEmployed by:'),]
```

```{r}
lm = d[,lm(num_subjective_comments ~ gender_shown + gender + age + years_programming + years_javascript + num_crs_per_week + education + employment + gender_shown*pct_men)]
getRobustCoefTest(lm)[c('gender_shownFemale', 'gender_shownFemale:pct_men'),]
```

```{r}
lm = d[,lm(num_subjective_comments ~ gender_shown + gender + age + years_programming + years_javascript + num_crs_per_week + education + employment + gender_shown*ratio_men_to_women)]
getRobustCoefTest(lm)[c('gender_shownFemale', 'gender_shownFemale:ratio_men_to_women'),]
```

## Are certain people more likely to remember gender?
```{r}
lm = d[,lm(correct_gender ~ gender_shown + is_reviewer_female + age + years_programming + years_javascript + num_crs_per_week + education + employment + pct_men)]
getRobustCoefTest(lm)
```

## Are certain people more likely to remember name?
```{r}
lm = d[,lm(correct_name ~ gender_shown + is_reviewer_female + age + years_programming + years_javascript + num_crs_per_week + education + employment + pct_men)]
getRobustCoefTest(lm)
```

## Placebo: are certain people more likely to remember app name?
```{r}
lm = d[,lm(correct_app ~ gender_shown + is_reviewer_female + age + years_programming + years_javascript + num_crs_per_week + education + employment + pct_men)]
getRobustCoefTest(lm)
```

## Placebo: are certain people more likely to remember company name?
```{r}
lm = d[,lm(correct_company ~ gender_shown + is_reviewer_female + age + years_programming + years_javascript + num_crs_per_week + education + employment + pct_men)]
getRobustCoefTest(lm)
```
